Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-17 ieee_paper.tex

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{figures/plot_for_natasha_ncar_end_of_year.pdf}

  \caption{Performance on a MIC of derivative computation for RBFFD
    with 884,736 nodes distributed quasi-randomly in a cube. Single
    derivative of a single function (base case, triangle) and four
    derivatives of four functions (multi case, circles). No bandwidth
    reduction (blue) and Reverse Cuthill-McKee (red).\todo{should we have a similar one for the host?}}
\end{figure}

>>>>

%<<<<<<< HEAD
%\begin{figure}
%  \centering
%  \includegraphics[width=.45\textwidth]{figures/plot_for_natasha_ncar_end_of_year.pdf}
%
%  \caption{Performance on a MIC of derivative computation for RBFFD
%    with 884,736 nodes distributed quasi-randomly in a cube. Single
%    derivative of a single function (base case, triangle) and four
%    derivatives of four functions (multi case, circles). No bandwidth
%    reduction (blue) and Reverse Cuthill-McKee (red).\todo{should we have a similar one for the host?}}
%\end{figure}
%
\begin{figure*}
\centering
\subfigure[Best case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_best-crop.pdf}} %\label{fig:ratio_best}}
\subfigure[Worst case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_worst-crop.pdf}}%\label{fig:ratio_worst}}
\subfigure[Worst case (No cacheline effects)]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_no_cache-crop.pdf}}%\label{fig:ratio_nocache}}
\caption{Ratio of flops to bytes; (a) simple count of flops and bytes that require transfer from memory;(b) best and (c) worst
case taking into account that bringing one element of $x$ into memory brings along the remainder of the cache line.}
\label{fig:ratio_bytes_flops}
\end{figure*}
%=======
%\begin{figure}
%  \centering
%  \includegraphics[width=.45\textwidth]{figures/plot_for_natasha_ncar_end_of_year.pdf}
%
%  \caption{Performance on a MIC of derivative computation for RBFFD
%    with 884,736 nodes distributed quasi-randomly in a cube. Single
%    derivative of a single function (base case, triangle) and four
%    derivatives of four functions (multi case, circles). No bandwidth
%    reduction (blue) and Reverse Cuthill-McKee (red).\todo{should we have a similar one for the host?}}
%\end{figure}
%
%>>>>>>> 619115cea6da9466f09a3b01456eacf7991606e2
